---
title             : "The long full title of your project"
shorttitle        : "Short title"

# Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
# The author and affiliation fields below where generated by
# Tenzing https://rollercoaster.shinyapps.io/tenzing/
author:
  - name: Ryan M. Straight
    affiliation: '1'
    role:                             
      - Conceptualization
      - Data curation
      - Writing - original draft
      - Writing - review & editing
    corresponding: yes
    email: ryanstraight@arizona.edu
    address: Enter postal address here
  - name: Author N. Two
    affiliation: '2'
    role:
      - Formal analysis
      - Methodology
      - Project administration
    email: email@email.com

affiliation:
  - id: '1'
    institution: University of Arizona
  - id: '2'
    institution: School of Hard Knocks


# Alter the authornote to meet your specifications
authornote: |
  This is the authornote for this document.
  
abstract: |
  `r lorem::ipsum(paragraphs = 1)`

keywords          : "project template, university of arizona, papaja, tinyverse"
wordcount         : "X"             # Update this when completed

bibliography      : ["r-references.bib", "refs.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes             # Leave this on until finished for easy line reference
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf

knit: (function(inputFile, encoding) {
          rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=paste('draft',sep=""))})
                        # Change "draft" in the line above
---

```{r setup, include = FALSE}
library("here")
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, message=FALSE, warning=FALSE)
```

```{r dataload, include=FALSE}
# Load your munge script, which imports data and cleans it
source(here("3-Study", "3-Data_Analysis", "munge.R"))

# Then load your exploratory data analysis
source(here("3-Study", "3-Data_Analysis", "eda.R"))

# And then load your plots
source(here("3-Study", "3-Data_Analysis", "plots.R"))
```


<!-- Here, provide information about your paper, what the reader can expect, and the construction and format of what’s to come. Give the reader whatever they need to understand the context of your project. -->

`r lorem::ipsum(paragraphs = 1)`

# Review of the literature

<!-- Give more detailed information about your topic of interest and examples of previous research that has been conducted on your topic. What impact did this research have in helping further understand your topic AND/OR what further questions about your topic did these prior research findings create? Be sure to properly cite the literature you found. Again, using BibTeX and papaja will make this considerably easier as it removes the guesswork. -->

`r lorem::ipsum(paragraphs = 5)`


# Research problem

<!-- Describe an area the needs to be further explored related to your topic of interest. State the research question that your statistical test can help answer. -->

`r lorem::ipsum(paragraphs = 1)`

# Design

The data used in this project is part of the `tidytuesday` project [@tidytuesday]^[Note that APA discourages the use of footnotes but you are not technically denied the option.]. R packages used in the analysis include: `r cite_r("r-references.bib")`.

<!-- Give information about where your data set came from and explain what inferential statistical test you are going to use. Describe the dataset structure and any relevant variables and scales. Leave no assumptions. -->

`r lorem::ipsum(paragraphs = 1)`

# Results

<!-- Describe the relevant descriptive statistics, the outcome of your inferential statistical test, and be sure to include the variables in your description. Don’t rely on tables and figures to do the explaining for you. -->

`r lorem::ipsum(paragraphs = 1)`

```{r}
# Display a plot from plots.R
carsplot
```

```{r}
# Pull in a table from the eda.R script
knitr::kable(cylindersummary)
```


# Discussion

<!-- What are the implications of your results? Did they surprise you? Do they support or contradict prior research findings related to your topic? -->

`r lorem::ipsum(paragraphs = 3)`



\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
